---
title: "KNN"
author: "Rafael"
date: "24 de septiembre de 2018"
output: html_document
---

Use the ISLR libary to get the iris data set. Check the head of the iris Data Frame.
```{r}
library(ISLR)
head(iris)
str(iris)
```

#Standardize Data
In this case, the iris data set has all its features in the same order of magnitude, but its good practice (especially with KNN) to standardize features in your data. Lets go ahead and do this even though its not 
necessary for this data!

Use scale() to standardize the feature columns of the iris dataset. Set this standardized version of the data as a new variable.
```{r}
standarized.iris <- scale(iris[ ,-5])
```

Check that the scaling worked by checking the variance of one of the new columns.
```{r}
print(var(standarized.iris[,2]))
```
Join the standardized data with the response/target/label column (the column with the species names).
```{r}
#The algorithm needs a different argument
myiris <- cbind(standarized.iris, iris[5])
```

Train and Test Splits
Use the caTools library to split your standardized data into train and test sets. Use a 70/30 split.

```{r}
library(caTools)
set.seed(101)
sample <- sample.split(myiris$Species, SplitRatio = 0.7)

train <- subset(myiris, sample == TRUE)
test <- subset(myiris, sample == FALSE)
```

Build a KNN model.
Call the class library.
```{r}
library(class)
```
Use the knn function to predict Species of the test set. Use k=1
```{r}
predicted.species <- knn(train[1:4], test[1:4], train$Species, k=1)
predicted.species
```
What was your misclassification rate?
```{r}
mean(test$Species != predicted.species)
```

#Choosing a K Value
Although our data is quite small for us to really get a feel for choosing a good K value, let's practice.

Create a plot of the error (misclassification) rate for k values ranging from 1 to 10.
```{r}
library(ggplot2)

prediction.series <- NULL
error.rate <- NULL

for (i in 1:10){
  set.seed(101)
  prediction.series <- knn(train[1:4], test[1:4], train$Species, k = i)
  error.rate[i] = mean(test$Species != prediction.series)
}

#Create a new data frame
k.values <- 1:10
error.df<- data.frame(error.rate, k.values)
head(error.df)

#Create the plot

ggplot(error.df, aes(x=k.values, y= error.rate)) +
  geom_point() +
  geom_line(lty = 'dotted', col ='red')


```

