---
title: "Logistic Regression Project"
author: "Rafael"
date: "14 de septiembre de 2018"
output: html_document
---

Get the Data
Read in the adult_sal.csv file and set it to a data frame called adult.
```{r}
adult <- read.csv("D:/Google Drive1/Eduación - cursos/R for data science/R-Course-HTML-Notes/R-Course-HTML-Notes/R-for-Data-Science-and-Machine-Learning/Training Exercises/Machine Learning Projects/CSV files for ML Projects/adult_sal.csv")
```

Check the head of adult
```{r}
head(adult)
```

You should notice the index has been repeated. Drop this column.
```{r}
library(dplyr)
adult <- select(adult, -X)
```

Check the head,str, and summary of the data now.
```{r}
head(adult)

str(adult)

summary(adult)
```

#Data Cleaning
Notice that we have a lot of columns that are cateogrical factors, however a lot of these columns have too many factors than may be necessary. In this data cleaning section we'll try to clean these columns up by reducing the number of factors.

type_employer column
Use table() to check out the frequency of the type_employer column.

```{r}
table(adult$type_employer)
```

How many Null values are there for type_employer? What are the two smallest groups?

There are 1836 Null values and the smallest groups are Never_worked and Without_pay

Combine these two smallest groups into a single group called "Unemployed". There are lots of ways to do this, so feel free to get creative. Hint: It may be helpful to convert these objects into character data types (as.character() and then use sapply with a custom function)

```{r}
#Function to melt two conditions
unemp <- function(job){
  job <- as.character(job)
  if (job == "Never-worked" | job == "Without-pay"){
    return('Unemployed')
  } else{
    return(job)
  }
}

adult$type_employer <- sapply(adult$type_employer, unemp)

```

What other columns are suitable for combining? Combine State and Local gov jobs into a category called SL-gov and combine self-employed jobs into a category called self-emp.

```{r}
state <- function(job){
  job <- as.character(job)
  if (job == "State-gov" | job == "Local-gov"){
    return('SL-gov')
  } else{
    return(job)
  }
}

adult$type_employer <- sapply(adult$type_employer, state)

self <- function(job){
  job <- as.character(job)
  if (job == "Self-emp-inc" | job == "Self-emp-not-inc"){
    return('self-emp')
  } else{
    return(job)
  }
}
adult$type_employer <- sapply(adult$type_employer, self)
```


#Marital Column
Use table() to look at the marital column
```{r}
table(adult$marital)
```

Reduce this to three groups:

-Married
-Not-Married
-Never-Married
```{r}
marital.fun <- function(marital){
  marital <- as.character(marital)
  if (marital == "Divorced" | marital == "Widowed" | marital =="Separated"){
    return('Not-Married')
  
  } else if (marital == "Married-AF-spouse"| marital == "Married-civ-spouse"| marital =="Married-spouse-absent") {
    return('Married')
  
  } else{
    return(marital)
  }
}
adult$marital <- sapply(adult$marital, marital.fun)
```

#Country Column¶
Check the country column using table()
```{r}
table(adult$country)
```

Group these countries together however you see fit. You have flexibility here because there is no right/wrong way to do this, possibly group by continents. You should be able to reduce the number of groups here significantly though.
```{r}
continent <- function(country){
  country <- as.character(country)
  
  if (country == "Cambodia" | country == "China" | country =="Hong" | country =="India" | country =="Iran" | country =="Japan"| country =="Laos"| country =="Philippines"| country =="Taiwan"|country =="Thailand"| country =="Vietnam"){
    return('Asia')
  
  } else if (country == "Canada"| country == "Mexico" | country =="United-States"| country == "Outlying-US(Guam-USVI-etc)") {
    return('North-America')
  
  } else if(country == "Columbia"| country == "Cuba" | country =="Dominican-Republic"| country == "Ecuador"| country == "El-Salvador"| country == "Guatemala"| country == "Haiti"| country == "Honduras"| country == "Jamaica"| country == "Nicaragua"| country == "Peru"| country == "Puerto-Rico"| country == "South"| country == "Trinidad&Tobago") {
    return('Central-Latin-America')
  } else if (country == "?"){
    return('Other')
  } else {
    return('Europe')
  }
}
adult$country <- sapply(adult$country, continent)
```

Check the str() of adult again. Make sure any of the columns we changed have factor levels with factor()

```{r}
str(adult)
adult$type_employer <- factor(adult$type_employer)
adult$country <- factor(adult$country)
adult$marital <-factor(adult$marital)

```
_______________
We could still play around with education and occupation to try to reduce the number of factors for those columns, but let's go ahead and move on to dealing with the missing data. Feel free to group thos columns as well and see how they effect your model.

Missing Data
Notice how we have data that is missing.

Amelia
Install and load the Amelia package.
```{r}
library(Amelia)
```

Convert any cell with a '?' or a ' ?' value to a NA value. Hint: is.na() may be useful here or you can also use brackets with a conditional statement. Refer to the solutions if you can't figure this step out.
```{r}
adult[adult == "?"] <- NA

```

Using table() on a column with NA values should now not display those NA values, instead you'll just see 0 for ?. Optional: Refactor these columns (may take awhile). For example:
```{r}
adult$occupation <- sapply(adult$occupation, factor)
adult$country <- sapply(adult$country, factor)
adult$type_employer <- sapply(adult$type_employer, factor)
adult$marital <- sapply(adult$marital, factor)

```

Play around with the missmap function from the Amelia package. Can you figure out what its doing and how to use it?
```{r}
library(Amelia)
missmap(adult, main = "adult data missing", col = c("red", "black"), legend = FALSE)

```
You should have noticed that using missmap(adult) is bascially a heatmap pointing out missing values (NA). This gives you a quick glance at how much data is missing, in this case, not a whole lot (relatively speaking). You probably also noticed that there is a bunch of y labels, get rid of them by running the command below. What is col=c('yellow','black') doing?

```{r}
missmap(adult,y.at=c(1),y.labels = c(''),col=c('yellow','black'))
```

Use na.omit() to omit NA data from the adult data frame. Note, it really depends on the situation and your data to judge whether or not this is a good decision. You shouldn't always just drop NA values.
```{r}
adult <- na.omit(adult)
str(adult)
```

Use missmap() to check that all the NA values were in fact dropped.
```{r}
missmap(adult,y.at=c(1),y.labels = c(''),col=c('yellow','black'))

```

#EDA
Although we've cleaned the data, we still have explored it using visualization.

Check the str() of the data
```{r}
str(adult)
```

Use ggplot2 to create a histogram of ages, colored by income.
```{r, message = FALSE}
library(ggplot2)
```

```{r}
#histogram of ages colored by income

ggplot(adult, aes(x=age)) + 
  geom_histogram(aes(fill = income), col = 'black', binwidth = 1) +
  theme_bw()

```

Plot a histogram of hours worked per week
```{r}
ggplot(adult, aes(x = hr_per_week)) +
  geom_histogram()
```

Rename the country column to region column to better reflect the factor levels.

```{r}
library(dplyr)
adult <- adult %>%
  mutate (region = country) %>%
  select(-country)
```

Create a barplot of region with the fill color defined by income class. Optional: Figure out how rotate the x axis text for readability
```{r}
ggplot()
```

