---
title: "Logistic Regression Project"
author: "Rafael"
date: "14 de septiembre de 2018"
output: html_document
---

Get the Data
Read in the adult_sal.csv file and set it to a data frame called adult.
```{r}
adult <- read.csv("D:/Google Drive1/Eduaci?n - cursos/R for data science/R-Course-HTML-Notes/R-Course-HTML-Notes/R-for-Data-Science-and-Machine-Learning/Training Exercises/Machine Learning Projects/CSV files for ML Projects/adult_sal.csv")
```

Check the head of adult
```{r}
head(adult)
```

You should notice the index has been repeated. Drop this column.
```{r}
library(dplyr)
adult <- select(adult, -X)
```

Check the head,str, and summary of the data now.
```{r}
head(adult)

str(adult)

summary(adult)
```

#Data Cleaning
Notice that we have a lot of columns that are cateogrical factors, however a lot of these columns have too many factors than may be necessary. In this data cleaning section we'll try to clean these columns up by reducing the number of factors.

type_employer column
Use table() to check out the frequency of the type_employer column.

```{r}
table(adult$type_employer)
```

How many Null values are there for type_employer? What are the two smallest groups?

There are 1836 Null values and the smallest groups are Never_worked and Without_pay

Combine these two smallest groups into a single group called "Unemployed". There are lots of ways to do this, so feel free to get creative. Hint: It may be helpful to convert these objects into character data types (as.character() and then use sapply with a custom function)

```{r}
unemp <- function(job){
  job <- as.character(job)
  if (job == "Never-worked" | job == "Without_pay"){
    return('Unemployed')
  } else{
    return(job)
  }
}

adult$type_employer <- sapply(adult$type_employer, unemp)

```

What other columns are suitable for combining? Combine State and Local gov jobs into a category called SL-gov and combine self-employed jobs into a category called self-emp.

```{r}
```


Marital Column
Use table() to look at the marital column

