---
title: "Tree Methods Project"
author: "Rafael"
date: "25 de septiembre de 2018"
output: html_document
---

Get the Data
Call the ISLR library and check the head of College (a built-in data frame with ISLR, use data() to check this.) Then reassign College to a dataframe called df
```{r}
library(ISLR)
df <- College
head(College)
library(dplyr)
```

EDA
Let's explore the data!

Create a scatterplot of Grad.Rate versus Room.Board, colored by the Private column.
```{r}
library(ggplot2)

ggplot(df)+ 
  geom_point(aes(x=Grad.Rate, y=Room.Board, col = Private)) + 
  theme_bw()
```

Create a histogram of full time undergrad students, color by Private.

```{r}
ggplot(df) + 
  geom_histogram(aes(x=F.Undergrad, fill = Private), col ='black', position = 'identity')
```

Create a histogram of Grad.Rate colored by Private. You should see something odd here.

```{r}
ggplot(df) + 
  geom_histogram(aes(x=Grad.Rate, fill = Private), col = 'black', position = 'stack') +
  theme_bw()
```

What college had a Graduation Rate of above 100% ?
```{r}
df[df$Grad.Rate>100,]
```

Change that college's grad rate to 100%
```{r}
df[df$Grad.Rate>100,]$Grad.Rate <- 100
```

Train Test Split
Split your data into training and testing sets 70/30. Use the caTools library to do this.

```{r}
library(caTools)

split <- sample.split(df$Private, SplitRatio = 0.7)

train <- subset(df, split == TRUE)
test <- subset(df, split == FALSE)
```

Decision Tree
Use the rpart library to build a decision tree to predict whether or not a school is Private. Remember to only build your tree off the training data.
```{r}
library(rpart)

tree <-rpart(Private~., method='class', data=train)

```

Use predict() to predict the Private label on the test data.

```{r}
prediction.tree <- predict(tree,test)
```

Check the Head of the predicted values. You should notice that you actually have two columns with the probabilities.
```{r}
head(prediction.tree)
```

Turn these two columns into one column to match the original Yes/No Label for a Private column.

```{r}

pred.df <- as.data.frame(prediction.tree) %>%
    mutate(Private = ifelse(as.data.frame(prediction.tree)$Yes>=as.data.frame(prediction.tree)$No, "Yes", "No"))
```

Now use table() to create a confusion matrix of your tree model.

```{r}
table(pred.df$Private, test$Private)
```

Use the rpart.plot library and the prp() function to plot out your tree model.

```{r}
library(rpart.plot)
prp(tree)
```

Random Forest
Now let's build out a random forest model!

Call the randomForest package library

```{r, message=FALSE}
library(randomForest)
```

Now use randomForest() to build out a model to predict Private class. Add importance=TRUE as a parameter in the model. (Use help(randomForest) to find out what this does.
```{r}
rfmodel <- randomForest(Private~., data = df, importance =TRUE)
```

What was your model's confusion matrix on its own training set? Use model$confusion.
```{r}
rfmodel$confusion
```

Grab the feature importance with model$importance. Refer to the reading for more info on what Gini[1] means.[2]
```{r}
rfmodel$importance
```

Predictions
Now use your random forest model to predict on your test set!
```{r}
rf.predict <- predict(rfmodel, test)
```

```{r}
table(rf.predict, test$Private)
```

