---
title: "Tree Methods Project"
author: "Rafael"
date: "25 de septiembre de 2018"
output: html_document
---

Get the Data
Call the ISLR library and check the head of College (a built-in data frame with ISLR, use data() to check this.) Then reassign College to a dataframe called df
```{r}
library(ISLR)
df <- College
head(College)
library(dplyr)
```

EDA
Let's explore the data!

Create a scatterplot of Grad.Rate versus Room.Board, colored by the Private column.
```{r}
library(ggplot2)

ggplot(College)+ 
  geom_point(aes(x=Grad.Rate, y=Room.Board, col = Private)) + 
  theme_bw()
```

Create a histogram of full time undergrad students, color by Private.

```{r}
ggplot(College) + 
  geom_histogram(aes(x=F.Undergrad, fill = Private), col ='black', position = 'identity')
```

Create a histogram of Grad.Rate colored by Private. You should see something odd here.

```{r}
ggplot(College) + 
  geom_histogram(aes(x=Grad.Rate, fill = Private), col = 'black', position = 'stack') +
  theme_bw()
```

What college had a Graduation Rate of above 100% ?
```{r}
College[College$Grad.Rate>100,]
```

Change that college's grad rate to 100%
```{r}
College[College$Grad.Rate>100,]$Grad.Rate <- 100
```

Train Test Split
Split your data into training and testing sets 70/30. Use the caTools library to do this.

```{r}
library(caTools)

split <- sample.split(College$Private, SplitRatio = 0.7)

train <- subset(College, split == TRUE)
test <- subset(College, split == FALSE)
```

Decision Tree
Use the rpart library to build a decision tree to predict whether or not a school is Private. Remember to only build your tree off the training data.
```{r}
library(rpart)

tree <-rpart(Private~., method='class', data=train)

```

Use predict() to predict the Private label on the test data.

```{r}
prediction.tree <- predict(tree, data=test)
```

Check the Head of the predicted values. You should notice that you actually have two columns with the probabilities.
```{r}
head(prediction.tree)
```

Turn these two columns into one column to match the original Yes/No Label for a Private column.

```{r}

pred.df <- as.data.frame(prediction.tree) %>%
    mutate(Private = ifelse(pred.df$Yes>pred.df$No, "Yes", "No"))
```

